Compilation With Program Synthesis

### 2023-09-07 new-paper/paper.tex
table comparing to Dargent
soundness
soundness appendix
formatting
abstract

\documentclass[acmsmall]{acmart}
\usepackage{graphicx}
\usepackage{proof}
\usepackage{stmaryrd}
\usepackage{amsmath}
%\usepackage{amssymb}
\usepackage{xcolor}
\usepackage{tcolorbox}
\usepackage{tikz}
\usepackage{tikz-cd}
\usepackage{syntax}
\usepackage{listings}
\usepackage{xspace}
\usepackage{mathtools}
\usepackage{mathpartir}
\lstset{basicstyle=\ttfamily, mathescape=true, literate={~} {$\sim$}{1}}

@@

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  Synthetic Separation Logic (SSL) is a specification language used by the \SuSLik{} program synthesis tool.
  \SuSLik{} will take a Hoare-style specification expressed in SSL and synthesize a program that satisfies this
  specification in a C-like language. However, these specifications are very low-level and SSL does not allow for much abstraction. In this paper,
  we explore a connection between SSL specifications and functional programming. We give a functional
  programming language, \Pika, which has both a standard semantics and a translation into SSL that respects the standard semantics. This translation also makes interfacing between SSL and \Pika{} easy. We introduce ``layouts'' to bridge the gap between a functional programming language and SSL called. This allows us to describe the memory layout of algebraic data types as SSL predicates inside \Pika.

  We then develop a second version of \Pika{} extended with an additional synthesis feature. These two versions are compared.

@@

@@

>>>>

\documentclass[acmsmall]{acmart}
\usepackage{graphicx}
\usepackage{proof}
\usepackage{stmaryrd}
\usepackage{amsmath}
%\usepackage{amssymb}
\usepackage{xcolor}
\usepackage{tcolorbox}
\usepackage{tikz}
\usepackage{tikz-cd}
\usepackage{syntax}
\usepackage{listings}
\usepackage{xspace}
\usepackage{mathtools}
\usepackage{mathpartir}
\usepackage{pifont}
\usepackage{thmtools}
\lstset{basicstyle=\ttfamily, mathescape=true, literate={~} {$\sim$}{1}}

@@

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  Synthetic Separation Logic (SSL) is a specification language used by the \SuSLik{} program synthesis tool.
  \SuSLik{} will take a Hoare-style specification expressed in SSL and synthesize a program that satisfies this
  specification in a C-like language. However, these specifications are very low-level and SSL does not allow for much abstraction. In this paper,
  we explore a connection between SSL specifications and functional programming. We give a functional
  programming language, \Pika, which has both a standard semantics and a translation into SSL that respects the standard semantics. This translation also makes interfacing between SSL and \Pika{} easy. We introduce ``layouts'' to bridge the gap between functional programming and SSL. This allows us to describe the memory layout of algebraic data types as SSL predicates inside \Pika.

  We then develop a second version of \Pika{} extended with an additional synthesis feature. This synthesis feature allows SSL propositions to be included in type signatures. Then, an implementation is synthesized from the type signature using \SuSLik. These two versions of \Pika{} are compared.

@@

\appendix

@@

\input{extended-soundness}
